Widely Bandwidth-Tunable Broadband Optical Filter on Silicon

### 2015-05-11 CacadedTunableFilter.tex
IgnoreFile

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\columnwidth]{data/FigApod}
  \caption{(Top)SEM photography of a part of the grating. The contra-directional coupler consists of two close waveguides of different width with periodic sidewall corrugations. (Bottom Left) Apodization profile of the grating. A larger coupling requires larger corrugations. (Bottom right) Average electric field in both waveguides. }
  \label{fig:SEM}
\end{figure}

@@

The device was fabricated using a CMOS-compatible technology with electron-beam lithography. 
Fiber grating couplers were used as optical IOs in the measurement. 
Fig.~\ref{fig:passive} shows the measured drop port response of the cascaded contra-DC filters. 
The measurements were normalized using the response of a pair of directly connected fiber grating couplers on the same chip.
\begin{figure}[htbp]
\centering
\includegraphics[width=.99\columnwidth]{data/Passive5NormNoSimu}
\caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz. The red line shows the averaged noise floor.}
\label{fig:passive}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\columnwidth]{data/FigApod}
  \caption{(a)SEM photography of a part of the grating. The contra-directional coupler consists of two close waveguides of different width with periodic sidewall corrugations. (b) Apodization profile of the grating. A larger coupling requires larger corrugations. (c) Intensity distributions of electrical fields of the first and second transverse modes. }
  \label{fig:SEM}
\end{figure}

@@

The device was fabricated using a CMOS-compatible technology with electron-beam lithography. 
Fiber grating couplers were used as optical IOs in the measurement. 
Fig.~\ref{fig:passive} shows the measured drop port response of the cascaded contra-DC filters. 
The measurements were normalized using the response of a pair of directly connected fiber grating couplers on the same chip.
\begin{figure}[htbp]
\centering
\includegraphics[width=.99\columnwidth]{data/Passive6}
\caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz.}
\label{fig:passive}
\end{figure}
